---
title: 'Correspondence Analysis'
author: 'Dataset tabella'
output:
  html_document: default
---
This dataset contains 5 rows and 10 columns.

- - -

```{r, echo = FALSE}
library(FactoMineR)
load('C:/Users/vito.tranquillo/Desktop/Git Projects/rotavirus/Workspace.RData')
```
### 1. Study of the outliers
The detection of outliers does not apply to CA results.

### 2. Inertia distribution
The inertia of the first dimensions shows if there are strong relationships between variables and suggests the number of dimensions that should be studied.

The first two dimensions of analyse express **95.23%** of the total dataset inertia ; that means that 95.23% of the rows (or columns) cloud total variability is explained by the plane.
This percentage is particularly high and thus the first plane perfectly represents the data variability.
This value is greater than the reference value that equals **87.84%**, the variability explained by this plane is thus significant
(the reference value is the 0.95-quantile of the inertia percentages distribution obtained by simulating 1703 data tables of equivalent size on the basis of a uniform distribution).

From these observations, it is absolutely not necessary to interpret the next dimensions.

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
par(mar = c(2.6, 4.1, 1.1, 2.1))
ggplot2::ggplot(cbind.data.frame(x=1:nrow(res$eig),y=res$eig[,2])) + ggplot2::aes(x=x, y=y)+ ggplot2::geom_col(fill="blue") + ggplot2::xlab("Dimension") + ggplot2::ylab("Percentage of variance") + ggplot2::ggtitle("Decomposition of the total inertia") + ggplot2::theme_light() + ggplot2::theme(plot.title = ggplot2::element_text(hjust =0.5)) + ggplot2::scale_x_continuous(breaks=1:nrow(res$eig))
```

**Figure 2 - Decomposition of the total inertia**
*The first factor is largely dominant: it expresses itself 81.99% of the data variability.*
*Note that in such a case, the variability related to the other components might be meaningless, despite of a high percentage.*

An estimation of the right number of axis to interpret suggests to restrict the analysis to the description of the first 1 axis.
These axis present an amount of inertia greater than those obtained by the 0.95-quantile of random distributions (81.99% against 63.03%).
This observation suggests that only this axis is carrying a real information.
As a consequence, the description will stand to these axis.

- - -

### 3. Description of the dimension 1

```{r, echo = FALSE, fig.align = 'center', fig.height = 3.5, fig.width = 5.5}
r.drawn <-
c(" sottoscrofa", " svezzamento", " ingrasso")
c.drawn <-
c("Clperfr_P", "Cldiff_P", "Brachyspira_pilos_P", "Brachyspira_hyod_P", 
"Lawsonia_P", "RVH_P", "RVC_P", "ecoli_P")
par(mar = c(4.1, 4.1, 1.1, 2.1))
plot.CA(res, selectRow = r.drawn, selectCol = c.drawn, axes = 1:2, choix = 'CA', invisible = c('var', 'quali'), title = '', cex = cex)
```

**Figure 3.1 - Overlayed factor map (CA)**
*The labeled rows are those with the higher contribution to the plane construction.*
*The labeled columns are those the best shown on the plane.*
